Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Added TextRank refference

\keywords{text summarization, NLP}

@@

\section{Introduction}
Abstractive text summarization is ...
as opposed to extractive summarization where

@@

\subsection{TextRank}
In this research we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score.

>>>>

\keywords{scientific text summarization, ROUGE, seq2seq, NLP, word embeddings}

@@

\section{Introduction}
Text summarization is a problem of

@@

\subsection{TextRank}
In this research we used a basic model TextRank as a baseline for comparison.  This is a graph method, influenced by PageRank algorithm, that represents the documents as a connected graph\cite{mihalcea-4}. We trained TextRank separately for each body of the paper and produced an extractive abstract-length summary. Scores were calculated on the basis of ROUGE score.
